\textbf{How open are hybrid journals included in transformative agreements?}

### 2024-09-12 analysis/manuscript.Rmd
Reviewer 1: Minor fix

The varying degrees of adoption of open access across the three major publishers can be attributed to distinct approaches to transformative agreements. 
Springer Nature, for example, started offering open access agreements for its hybrid journal portfolio to selected consortia such as the Max Planck Society, the Swedish Bibsam Consortium and the Finnish FinELib consortium in 2015 under the name Springer Compact[^springercompact]. 
Prior to this, Springer had some pilot agreements with a small number of institutions, including the University of Göttingen [@Schmidt_2012].
However, the Springer Compact agreements were not included in the data as they concluded before the start of the transformative agreement data collection in June 2021. 
Nonetheless, the results demonstrate the importance of agreements for Springer Nature's hybrid open access business over the past five years (Figure \ref{fig:publisher_figure}).
In 2022, `r publisher_summary_df |> filter(cr_year == "2022", publisher == "Springer Nature", type == "ta_oa") |> pull(value) / publisher_summary_df |> filter(cr_year == "2022", publisher == "Springer Nature") |> pull(value) |> sum()*100`% (n = `r  publisher_summary_df |> filter(cr_year == "2022", publisher == "Springer Nature", type == "ta_oa") |> pull(value)`) of open access in Springer Nature hybrid journals was enabled through transformative agreements.
In the same year, `r publisher_summary_df |> filter(cr_year == "2022", publisher == "Wiley", type == "ta_oa") |> pull(value) / publisher_summary_df |> filter(cr_year == "2022", publisher == "Wiley") |> pull(value) |> sum()*100`% (n = `r publisher_summary_df |> filter(cr_year == "2022", publisher == "Wiley", type == "ta_oa") |> pull(value)`) of Wiley's open access articles could be linked to transformative agreements in 2022. 
By contrast, Elsevier published fewer than half of its open access articles through transformative agreements (n = `r publisher_summary_df |> filter(cr_year == "2022", publisher == "Elsevier", type == "ta_oa") |> pull(value) `; `r publisher_summary_df |> filter(cr_year == "2022", publisher == "Elsevier", type == "ta_oa") |> pull(value) / publisher_summary_df |> filter(cr_year == "2022", publisher == "Elsevier") |> pull(value) |> sum()*100`%).

>>>>

The varying degrees of adoption of open access across the three major publishers can be attributed to distinct approaches to transformative agreements. 
Springer Nature, for example, started offering open access agreements for its hybrid journal portfolio to selected consortia such as the Max Planck Society, the Swedish Bibsam Consortium and the Finnish FinELib consortium in 2015 under the name Springer Compact[^springercompact]. 
Prior to this, Springer had some pilot agreements with a small number of institutions, including the University of Göttingen [@Schmidt_2012].
However, the Springer Compact agreements were not included in the data as they concluded before the start of the transformative agreement data collection in June 2021. 
Nonetheless, the results demonstrate the importance of agreements for Springer Nature's hybrid open access business over the past five years (Figure \ref{fig:publisher_figure}).
In 2022, `r publisher_summary_df |> filter(cr_year == "2022", publisher == "Springer Nature", type == "ta_oa") |> pull(value) / publisher_summary_df |> filter(cr_year == "2022", publisher == "Springer Nature") |> pull(value) |> sum()*100`% (n = `r  publisher_summary_df |> filter(cr_year == "2022", publisher == "Springer Nature", type == "ta_oa") |> pull(value)`) of open access in Springer Nature hybrid journals was enabled through transformative agreements.
In the same year, `r publisher_summary_df |> filter(cr_year == "2022", publisher == "Wiley", type == "ta_oa") |> pull(value) / publisher_summary_df |> filter(cr_year == "2022", publisher == "Wiley") |> pull(value) |> sum()*100`% (n = `r publisher_summary_df |> filter(cr_year == "2022", publisher == "Wiley", type == "ta_oa") |> pull(value)`) of Wiley's open access articles could be linked to transformative agreements. 
By contrast, Elsevier published a comparatively lower proportion of its open access articles through transformative agreements in 2022 (n = `r publisher_summary_df |> filter(cr_year == "2022", publisher == "Elsevier", type == "ta_oa") |> pull(value) `; `r publisher_summary_df |> filter(cr_year == "2022", publisher == "Elsevier", type == "ta_oa") |> pull(value) / publisher_summary_df |> filter(cr_year == "2022", publisher == "Elsevier") |> pull(value) |> sum()*100`%).
